\documentclass{ximera}

\input{../preamble.tex}

\title{Continuity and the Intermediate Value Theorem}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}
After completing this section, students should be able to do the following.

\begin{itemize}
\item Identify where a function is, and is not, continuous.
\item Understand the connection between continuity of a function and
  the value of a limit.
\item Make a piecewise function continuous.
\item State the Intermediate Value Theorem including hypotheses.
\item Determine if the Intermediate Value Theorem applies.
\item Sketch pictures indicating why the Intermediate Value Theorem is
  true, and why all hypotheses are necessary.
\item Explain why certain points exist using the Intermediate Value
  Theorem.
\item Bisection method.
\end{itemize}

\end{sectionOutcomes}

\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item Domain
    \item Range
    \item Piece-wise functions
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.

\end{document}
