\documentclass{ximera}

\input{../preamble.tex}

\title{Using limits to detect asymptotes}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}

After completing this section, students should be able to do the following.

\begin{itemize}
\item Recognize when a limit is indicating there is a vertical asymptote.
\item Evaluate the limit as $x$ approaches a point where there is a vertical asymptote.
\item Match graphs of functions with their equations based on vertical asymptotes.
\item Discuss what it means for a limit to equal $\infty$.
\item Define a vertical asymptote.
\item Find horizontal asymptotes using limits.
\item Produce a function with given asymptotic behavior.
\item Recognize that a curve can cross a horizontal asymptote.
\item Understand the relationship between limits and vertical asymptotes.
\item Calculate the limit as $x$ approaches $\pm \infty$ of common functions algebraically.
\item Find the limit as $x$ approaches $\pm \infty$ from a graph.
\item Define a horizontal asymptote.
%%\item Define a slant asymptote.
%%\item Approximate a slant asymptote from the graph of a function.
%%\item Find slant asymptotes algebraically and graphically.
\item Compute limits at infinity of famous functions.
\item Find vertical asymptotes of famous functions.
\item Identify horizontal asymptotes by looking at a graph.
\item Identify vertical asymptotes by looking at a graph.
%%\item Identify slant asymptotes by looking at a graph.
\end{itemize}
\end{sectionOutcomes}

\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Rational functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/reviewOfFamousFunctions/digInRationalFunctions}%%
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.


\end{document}
