\documentclass{ximera}

\input{../preamble.tex}

\title{Limit laws}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}
After completing this section, students should be able to do the following.

\begin{itemize}
\item Define continuity in terms of limits.
\item Calculate limits using the limit laws.
\item Understand that famous functions are continuous on their domains. 
\item Calculate limits by replacing a function with a continuous
  function.
\item Understand the Squeeze Theorem and how it can be used to find limit values.
\item Calculate limits using the Squeeze Theorem.
\end{itemize}
\end{sectionOutcomes}

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Understanding functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/understandingFunctions/digInForEachInputExactlyOneOutput}%%
    \item Domain
    \item Absolute value
    \item \link[Inequalities]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/prerequisiteVideos/algebraInequalities}
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.

\end{document}
